High Contrast Coronagraphy

### 2024-09-17 src/tex/ms.tex
removed table

%The scale invariant phase masks of these two coronagraphs are shown in Figure \ref{fig:scale_invariant}.

% \begin{figure}[ht]
%   \centering
%   \script{plot_scale_invariant_masks.py}
%   \includegraphics[width=0.5\linewidth]{figures/scale_invariant_masks.pdf}
%   \caption{The focal plane phase functions of two scale invariant coronagraphs.
%   %
%   The left figure shows the four quadrant phase mask and the right figure shows the optical vortex phase mask.}
%   \label{fig:scale_invariant}
% \end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{3}{c}{Comparison of \acs{ppm} and \acs{fpm} coronagraphs} \\[.5\normalbaselineskip]
     & \acl{fpm} & \acl{ppm} \\
    \midrule
    Advantages \\
     & \tabitem Small IWA & \tabitem Pointing invariant \\
     & \tabitem High transmission & \tabitem Single optic \\
     & \tabitem 360 deg FOV & \tabitem Any telescope mirror geometry \\
    Disadvantages \\
     & \tabitem Star diameter leakage & \tabitem Complex manufacture \\
     & \tabitem Pointing sensitive & \tabitem Larger IWA \\
     & \tabitem Complex design with tel pupils & \tabitem Lower planet throughput \\
     & \tabitem Lyot stop required & \tabitem Smaller FOV \\[.5\normalbaselineskip]
    \bottomrule
  \end{tabular}
\end{table}

>>>>

@@

% \begin{table}
%   \centering
%   \label{asdf}
%   \begin{tabular}{lll}
%     \toprule
%     \multicolumn{3}{c}{Comparison of \acs{ppm} and \acs{fpm} coronagraphs} \\[.5\normalbaselineskip]
%      & \acl{fpm} & \acl{ppm} \\
%     \midrule
%     Advantages \\
%      & \tabitem Small IWA & \tabitem Pointing invariant \\
%      & \tabitem High transmission & \tabitem Single optic \\
%      & \tabitem 360 deg FOV & \tabitem Any telescope mirror geometry \\
%     Disadvantages \\
%      & \tabitem Star diameter leakage & \tabitem Complex manufacture \\
%      & \tabitem Pointing sensitive & \tabitem Larger IWA \\
%      & \tabitem Complex design with tel pupils & \tabitem Lower planet throughput \\
%      & \tabitem Lyot stop required & \tabitem Smaller FOV \\[.5\normalbaselineskip]
%     \bottomrule
%   \end{tabular}
% \end{table}
